---
title: "Shiny dashboard development notebook"
author: "Dylan Lewis"
output:
  html_document: 
    toc: true
    toc-location: left
---

# Development notebook

I will use this .rmd doc to develop (mostly back-end) functions for the app. Finished functions will live in the /r/ folder.

```{r setup, include = FALSE}
knitr::opts_chunk$set("echo" = TRUE)
library(tidyverse)
dataPath <- "C:/Users/2808003l/Documents/Sipher"
```

## Data Prep

### Aggregated data

Data is currently aggregated at three resolutions: country, local authority, LSOA

```{r load aggregated data}
#read country data
ctrDat <- read_csv(paste0(dataPath, "/ROutput/ctr_export_labels.csv"),
                     show_col_types = FALSE) %>% rename_with(~str_remove(.x, "_label"))
# ctrRaw <- read_csv(paste0(dataPath, "/ROutput/ctr_code_export.csv"),
#                     show_col_types = FALSE)
# ctrDat <- ctrRaw %>% select(!c("ctr_code", "value")) %>% cbind(., ctrLabelled)
 glimpse(ctrDat)

#read local autority data
ladDat <- read_csv(paste0(dataPath, "/ROutput/lad_export_labels.csv"),
                    show_col_types = FALSE) %>% rename_with(~str_remove(.x, "_label"))
glimpse(ladDat)

# read LSOA (2021) data
#lsoaDat <- read_csv(paste0(dataPath, "/ROutput/lsoa21_export_labels.csv"),
#                    show_col_types = FALSE) %>% rename_with(~str_remove(.x, "_label"))
#glimpse(lsoaDat)

#read ward data
wardDat <- read_csv(paste0(dataPath, "/ROutput/ward_export_labels.csv"),
                    show_col_types = FALSE) %>% rename_with(~str_remove(.x, "_label"))
glimpse(wardDat)

#read GB data
gbDat <- read_csv(paste0(dataPath, "/ROutput/gb_export_labels.csv"),
                    show_col_types = FALSE) %>% rename_with(~str_remove(.x, "_label"))
glimpse(gbDat)
```

### Geo lookup

```{r load geo link}
#lookupFiles <- map(list.files(paste0(dataPath, "/geo_lookup/"), full.names = T), read.csv)
#names(lookupFiles) <- map_chr(list.files(paste0(dataPath, "/geo_lookup/")), ~str_remove_all(.x, "[() ]|(.csv)"))
#names(lookupFiles)
lookup <- read_csv(paste0(dataPath, "/geo_lookup/PCD_OA21_LSOA21_MSOA21_LAD_NOV23_UK_LU.csv"),
                   show_col_types = FALSE)
```

Create a nested list to identify parent/child areas

```{r lookup list}

lookupCodes <- lookup %>%
  select(ladcd, ladnm, lsoa21cd) %>%
  mutate(ctr = str_sub(lsoa21cd, 1, 1),
         ctrnm = case_match(ctr,
                           "E" ~ "England",
                           "W" ~ "Wales",
                           "S" ~ "Scotland"),
         .before = ladcd) %>%
  filter(ctr %in% c("E", "W", "S"))

lookupList <- lookupCodes %>% nest(.by = c(ctr:ladnm), .key="lsoa") %>% nest(.by=c(ctr, ctrnm), .key="lad")

#lookupList.RData is added to /data/ folder
```

Not sure if a list is a good approach...
Also this lookup file is for LSOA->LAD->Country, we want Ward->LAD->Country

```{r lookup 2}
# lookup file for wards
lookup_wd_lad <- read_csv(paste0(dataPath, "/geo_lookup/Ward_to_Local_Authority_District_(December_2022)_Lookup_in_the_United_Kingdom.csv"),
                   show_col_types = FALSE)

lookup_wd_lad <- lookup_wd_lad %>% select(ward = WD22CD, ward_name = WD22NM, lad = LAD22CD, lad_name = LAD22NM)
```


### Shapefiles
Load in shapefiles, filter for LADs available in data
```{r load in shapefiles}
library(sf)
ladSF_raw <- sf::read_sf(paste0(dataPath, "/topo/Local_Authority_Districts/LAD_DEC_2021_GB_BUC.shp"))
wardSF_raw <- sf::read_sf(paste0(dataPath, "/topo/Wards/WD_DEC_22_GB_BSC.shp"))
#remove areas not in dataset
ladSF <- ladSF_raw %>%
  filter(LAD21CD %in% unique(ladDat$lad)) %>%
  rename(lad_name = LAD21NM,
         lad = LAD21CD,
         lad_welsh = LAD21NMW)
wardSF <- wardSF_raw %>%
  filter(WD22CD %in% unique(wardDat$ward)) %>%
  rename(ward_name = WD22NM,
         ward = WD22CD,
         ward_welsh = WD22NMW)
#ggplot(data=ladSF) +geom_sf()
# usethis::use_data(ladSF, overwrite = T)
# usethis::use_data(wardSF, overwrite = T)
```


### Code book
create codebook to lookup variable names and levels
```{r codebook}
codebook <- read.csv(paste0(dataPath,
                            "/codebook/codebook.csv"))
codebook <- codebook %>% 
  nest_by(obs, .key = "cat") %>%
  mutate(mean = ifelse(nrow(cat)==1, T, F))#%>%
#   mutate(section = case_match(obs,
#                               c("employment status",
#                                 "highest educational qualification",
#                                 "marital status",
#                                 "ethnicity",)
#                               ))

```

### testing maps
```{r}
testSF <- wardSF %>% filter(WD23CD %in% lookup_wd_lad$WD23CD[lookup_wd_lad$LAD23CD=="E06000001"])
plot(testSF)
```

