---
title: "Shiny dashboard development notebook"
author: "Dylan Lewis"
output:
  html_document: 
    toc: true
    toc-location: left
---

# Development notebook

I will use this .rmd doc to develop (mostly back-end) functions for the app. Finished functions will live in the /r/ folder.

```{r setup, include = FALSE}
knitr::opts_chunk$set("echo" = TRUE)
library(tidyverse)
dataPath <- "C:/Users/2808003l/Documents/Sipher"
```

## Data Prep

### Aggregated data

Data is currently aggregated at three resolutions: country, local authority, LSOA

```{r load aggregated data}
#read country data
ctrDat <- read_csv(paste0(dataPath, "/ROutput/ctr_code_export.csv"),
                    show_col_types = FALSE)
glimpse(ctrDat)
#read local autority data
ladDat <- read_csv(paste0(dataPath, "/ROutput/lad_export.csv"),
                    show_col_types = FALSE)
glimpse(ladDat)
# read LSOA (2011) data
#lsoaDat <- read_csv(paste0(dataPath, "/ROutput/lsoa11_export.csv"),
#                    show_col_types = FALSE)
#glimpse(lsoaDat)

wardDat <- read_csv(paste0(dataPath, "/ROutput/ward_export.csv"),
                    show_col_types = FALSE)
glimpse(wardDat)
```

### Geo lookup

```{r load geo link}
#lookupFiles <- map(list.files(paste0(dataPath, "/geo_lookup/"), full.names = T), read.csv)
#names(lookupFiles) <- map_chr(list.files(paste0(dataPath, "/geo_lookup/")), ~str_remove_all(.x, "[() ]|(.csv)"))
#names(lookupFiles)
lookup <- read_csv(paste0(dataPath, "/geo_lookup/PCD_OA21_LSOA21_MSOA21_LAD_NOV23_UK_LU.csv"),
                   show_col_types = FALSE)
```

Create a nested list to identify parent/child areas

```{r lookup list}

lookupCodes <- lookup %>%
  select(ladcd, ladnm, lsoa21cd) %>%
  mutate(ctr = str_sub(lsoa21cd, 1, 1),
         ctrnm = case_match(ctr,
                           "E" ~ "England",
                           "W" ~ "Wales",
                           "S" ~ "Scotland"),
         .before = ladcd) %>%
  filter(ctr %in% c("E", "W", "S"))

lookupList <- lookupCodes %>% nest(.by = c(ctr:ladnm), .key="lsoa") %>% nest(.by=c(ctr, ctrnm), .key="lad")

#lookupList.RData is added to /data/ folder
```

Not sure if a list is a good approach...
Also this lookup file is for LSOA->LAD->Country, we want Ward->LAD->Country

```{r lookup 2}
# lookup file for wards
lookup_wd_lad <- read_csv(paste0(dataPath, "/geo_lookup/Ward_to_Local_Authority_District_to_County_to_Region_to_Country_(May_2023)_Lookup_in_United_Kingdom.csv"),
                   show_col_types = FALSE)

lookup_wd_lad <- lookup_wd_lad %>% select(WD23CD, WD23NM, LAD23CD, LAD23NM, CTRY23CD, CTRY23NM)
```


### Shapefiles
Load in shapefiles, filter for LADs available in data
```{r load in shapefiles}
library(sf)
ladSF <- sf::read_sf(paste0(dataPath, "/topo/Local_Authority_Districts/LAD_DEC_2023_UK_BSC.shp"))
wardSF <- sf::read_sf(paste0(dataPath, "/topo/Wards/WD_DEC_2023_UK_BSC.shp"))
#remove NI LADs
ladSF <- ladSF %>% filter(LAD23CD %in% unique(ladDat$lad))
wardSF <- wardSF %>% filter(WD23CD %in% unique(wardDat$ward))
#ggplot(data=ladSF) +geom_sf()
# problem!! these are not 2011 shapefiles, so some are missing
```


### Code book
create codebook to lookup variable names and levels
```{r codebook}
codebook <- ctrDat %>%
  select(obs, cat) %>%
  unique() %>%
  nest_by(obs, .key = "cat")
#can add names later
```

### testing maps
```{r}
testSF <- wardSF %>% filter(WD23CD %in% lookup_wd_lad$WD23CD[lookup_wd_lad$LAD23CD=="E06000001"])
plot(testSF)
```

