---
title: "SIPHERdashboard"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SIPHERdashboard}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SIPHERdashboard)
```

This dashboard enables users to explore the SIPHER Synthetic
             Population for Individuals in Great Britain, 2019-2021. For this
             purpose, we have linked the SIPHER Synthetic Population dataset with
             Understanding Society survey data for individuals and households,
             and created an aggregated version of the resulting linkage. Once
             linked with Understanding Society survey data, the SIPHER Synthetic
             Population provids a “digital twin” of the adult population in Great
             Britain. This enables the dataset to support a wide range of applications
             across policy and research. These applications can include
             exploratory analyses of small areas such as census output areas or
             electoral wards, supplementing traditional administrative sources
             of data. In addition, the SIPHER Synthetic Population can serve as
             an input for microsimulation models through the provision of
             high-quality information on individuals and areas at a granular
             spatial resolution. Capturing multiple key life domains, this
             dashboard allows for an intuitive exploration of spatial patterns
             at different layers of geography. Please note that this dashboard
             does not contain or present any individual-level data.
